\chapter*{Conclusions}\label{chap:conclusions}

A search for the exclusive decays of the Higgs boson to a photon and either a $\phi(1020)$, $\omega(782)$ or $\text{D}^{*}(2007)^{0}$ meson, with subsequent decays into a charged pair and neutral particles, has been presented. These decays have been suggested as a probe of the Higgs boson couplings to light quarks and as a test of potential deviations from the Standard Model prediction in these flavour interactions. The four decay channels explored are: $\text{H}\decaysto \phi\gamma$ with further $\phi\decaysto \pi^+\pi^-\pi^0$, $\text{H}\decaysto \omega\gamma$ with further $\omega\decaysto \pi^+\pi^-\pi^0$, $\text{H}\decaysto \text{D}^{*0}\gamma$ with further $\text{D}^{*0}\decaysto \text{D}^{0}\pi^{0}/\gamma$, $\text{D}^{0}\decaysto K^{-}\pi^{+}$ and $\text{H}\decaysto \text{D}^{*0}\gamma$ with further $\text{D}^{*0}\decaysto \text{D}^{0}\pi^{0}/\gamma$, $\text{D}^{0}\decaysto K^{-}\pi^{+}\pi^{0}$. The analysis is performed with a pp collision data sample corresponding to an integrated luminosity of 39.54 fb$^{-1}$ collected at $\sqrt{s}=$13 TeV with the CMS detector at the LHC in 2018 during Run 2. The background model is derived using a fully data driven approach, and thus is MC independent.

The final expected upper limits on the branching ratio of the studied decays are reported in Table \ref{tab:results}, and are:
\begin{equation*}
    \begin{aligned}
        \mathcal{B}(\text{H}\decaysto \phi\gamma) <&\ 1.969 \times 10^{-2}\\
        \mathcal{B}(\text{H}\decaysto \omega\gamma) <&\ 2.867 \times 10^{-3}\\
        \mathcal{B}(\text{H}\decaysto\text{D}^{*0}\gamma) <&\ 7.403 \times 10^{-3}\\
        \mathcal{B}(\text{H}\decaysto\text{D}^{*0}\gamma) <&\ 1.268 \times 10^{-2}\\
\end{aligned}
\end{equation*}
where the first $\text{H}\decaysto\text{D}^{*0}\gamma$ corresponds to the channel where $\text{D}^{*0}\decaysto \text{D}^{0}\pi^{0}/\gamma$, $\text{D}^{0}\decaysto K^{-}\pi^{+}$.

The first upper limit relies on a different meson decay mode than the one used in Ref. \cite{ATLAS:2017gko}. Combining both channels will further constrain this upper bound. Conversely, upper limits on the decay mode $\text{H}\decaysto\text{D}^{*0}\gamma$ have never been computed before. This initial approach can be improved and optimized to further constrain the branching ratio of this decay.

This analysis has applied new approaches in the context of these searches. These include the Boosted Decision Tree regression for the transverse momentum of each meson, as well as other techniques attempted to reconstruct the $\pi^0$. Additionally, the two-dimensional fit has proved to significantly reduce the limit, thereby opening the door to more applications in similar studies.

\clearpage{\thispagestyle{empty}}
